### 2023-01-27 article.tex
Progress

Nowadays, the lack of paradata can be seen as 'a drastic constraint'
in data use \cite{huvila2022improving}.
Computer code, being paradata, the effect of its absence is, most obviously,
that a computational experiment cannot be redone 
easily,
yet there are wider implications as well.

>>>>

A recent paper explores the use of paradata to increase the impact of data,
stating that lack of paradata can be seen as 'a drastic constraint'
in the use of data and offer some suggestions to 
make paradata useful for data re(use):
paradata should be comprehensive, comprehensively documentated
and be friendly to computers \cite{huvila2022improving}.
These suggestions appear to work with code as well,
where these suggestions show up as best practices (such
as \cite{stodden2013best}), some of which
described below.
The lack of computer code is just as much a drastic constraint
in the use of a scientific experiment.
The clearest effect of its absence is, most obviously,
that a computational experiment cannot be redone 
easily, yet there are wider implications, described below, as well.
